What is an Ancestral Recombination Graph?

### 2022-03-02 paper.tex
Mention optional 3rd change to make a 2-recombination node ARG
Fixes #128 with the rough text Jerome suggested.
Changes for fig3 caption

\begin{figure}
\begin{center}
    \includegraphics[width=\textwidth]{illustrations/arg-in-pedigree}
\end{center}
\caption{\label{fig-arg-in-pedigree}
% TODO caption needs another pass. One the full section has been written
% it'll be clearer what we need to say in the caption vs the text.
The Ancestral Recombination Graph defined as arbitrary inheritance
of genomes between diploid (or any ploidy; see text) individuals.
(A) Each individual consists of two genomes, and each genome is
inherited as a (potentially) recombinant mixture of the individual's parent's
genomes. (B) Genomes are modelled as nodes in a graph, and the edges
denote inheritance. Each edge is annotated with genome coordinates
defining the specific region(s) inherited.
(C) This description of inheritance fully defines the
local relationships along the genome, as shown in the local
or ``marginal'' trees.
}
\end{figure}

>>>>

\begin{figure}
\begin{center}
    \includegraphics[width=\textwidth]{illustrations/arg-in-pedigree}
\end{center}
\caption{\label{fig-arg-in-pedigree}
% TODO caption needs another pass. One the full section has been written
% it'll be clearer what we need to say in the caption vs the text.
The Ancestral Recombination Graph defined in terms of genomes embedded
in a pedigree. (a) Diploid individuals, visualised in a highly inbred pedigree and
labelled $i_1$ to $i_8$, contain both paternal (left) and maternal (right) genomes
labelled \textsf{A} to \textsf{P}. Black lines show transmission paths connecting
genomes in the current generation (\textsf{A} to \textsf{D}) with their ancestors.
Two recombination breakpoints, at positions 3 and 6 mean that genomes \textsf{A}
and \textsf{C} are independent recombinants of the paternal genomes \textsf{E}
and \textsf{F}: the region of genome transmitted through each edge is shown in
these cases. Where genomes merge into a common ancestor, the merged region
is shown darker, until all genomic regions are fully coalesced in genome \textsf{N}
(b) The equivalent genome ARG, where there is a single type of node (representing
a genome) along with annotations on all edges; annotations showing partial
transmission are highlighted in bold. Recombination, such as that causing the
breakpoint at position 3, is associated with two parent genomes (\textsf{E} and 
\textsf{F}) and a child genome (the recombinant, \textsf{A}).
(c) The edge-annotated genome ARG in (b) fully defines the
local relationships along the genome, as shown in the local
or ``marginal'' trees.
}
\end{figure}
